### 2015-11-04 CVPR16/Source/experiments.tex
Update Association Experiment

For each sequence of the KITTI dataset, the methods of \cite{} and \cite{} are used respectively for computing detection bounding boxes and object tracklets. We then apply \cite{} on object tracklets to extract point tracks. From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favor dynamic scenes). In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probablity) and the baseline method (for depth ordering).

Figure~\ref{fig:assoc-occ-results} presents the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset. From these results, our method consistently achieves the lowest mean errors, followed by the bounding box baseline method, which clearly shows the advantage of our continous occlusion model. The mean errors of BM and RAS are comparable and among the highest ones.

>>>>

For each sequence of the KITTI dataset, the methods of \cite{} and \cite{} are used respectively for computing detection bounding boxes and object tracklets. We then apply \cite{} on object tracklets to extract point tracks. From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes). In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).

Figure~\ref{fig:assoc-occ-results} presents the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset. From the results, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. Both RAS and BM often have the highest errors and hence the highest mean errors on all sets of input point tracks.
